\chapter{Killing the Mansion}

It is often claimed that one's life flashes before one's eyes when they
are dying. And as I sit here with all these wounds, it seems to be true,
at least partially, because I indeed am dying, but my life didn't
``flash before my very eyes'', only the events of the last six hours. It
began at one of the many extravagant, some may call them quite decadent,
masked soiree. During one of many such a party, befell me a curious
encounter. Footsteps I did hear, very calculated, profoundly precise.
The type of profoundness that disturbs the mind and seizes attention.
Soon the proprietor of the disconcerting step showed herself. She
approached and introduced herself as Elisabeth maiden to the Jadewill
mansion. I retorted as is expected of me in this company. I was bid to
be a guest at yet another gala and of course, with my then lavish
manners, I accepted hastily. As soon as I did, without a second word the
maiden walked away. Disappearing in the crowd as abruptly as she had
come. At the time I thought nothing of it.

Soon I came about my old friend Clerval with whom I spent most my time,
he is a tremendously learned scholar and speaks to that accord, I bear a
strange liking to him. Angell was absorbed into this style of life with
me as the primary catalyst. Clerval bowed, I rebound with a gesture of
the hand and the greeting was over. We exchanged thoughts on the night
and Clerval inadvertently mentions Elisabeth's invitation. And so I
inquire, ``Clerval, did you obey the invitation?''. ``No, for I fought
the invitation and overcame it.''

Walking home that night, roaming around former St.~Stephen's tower, I
saw a White raven roost, its patchy skin imperceptible through its white
veil of feathers. Back home promptly after I retired to my room and bed,
I was awoken by a loud reverberation of all six walls and a pleasant
illumination coming from across the room, breaking through the blinding
darkness. Donned my gown I reach out my hand to the handle of a door
that seems to be the source of the glow. The moment my hand makes
contact with the door, I find myself before an Elizabeth stood in the
doorframe. She beckons me toward my dresser and utters that they shall
be waiting outside. Once through my front door, I enter a red and black
checkered little lounge, with a sofa in the centre and a newspaper with
a wineglass by the side. Sitting down, turning to the page with the
wineglass, I notice a drop of wine not from ink had appeared on my page.
One glance upward yielded the answer to that question, Clerval was
sitting there with a wineglass in his hand, having just spilt some. With
haste, I received an apology for the potential danger he had posed to my
suit, nevertheless interrupted by a quiet Elisabeth we were each led
back out our respective door.

We found ourselves standing in a tremendous amphitheatre headed by
several grand figures. A strikingly tall man, with great muscle, his
long silvery hair skillfully done into a wavy ponytail protruding from
his ruffled hair, and a beautifully white old shirt, decorated in red by
flowery etchings. He greets us with wide gestures, welcoming us to the
Jadewill family Mansion. Introduces himself as Astrophel, next pointing
to a pair of young girls dressed in little black dresses, whose names
are apparently Callidora and Lucilla. The latter seeming slightly off.
With the realisation that Callidora is not indeed alive, rather propped
up with strings, came a powerful sense of Astrophel's wish of silence
about the matter. You've already met Elisabeth, and Saber will show
himself in due time. We've invited you here to celebrate Callidora's
anniversary, and so we'll partake in a night of games. Each resident
having prepared something that you may play, everyone else shall watch
and enjoy themselves.

It is midnight, Let the games begin!

Lucian finds himself in a library. Not many people make up the current
inhabitants of said library. One does approach Lucian and inquires,
``Kind sir, would you mind dividing these digits into two groups?''.
Lucian replies with, ``I shall name them M and F.''.

1F
2F
3M
4F
5F
6M
7F
8M
9M

``Correct!'', exclaims the man, ``and for that, I shall shoot you.''.
``do not be hasty close friend'', replies Lucian drawing a sword. But
haste did overpower the men, and a shot was fired. Lucian stood there
with a bullet wound in his heart, which curiously returned back from
whence it came, the damage having healed completely. A shot man dropped
the sword and proclaimed, ``For now that I am dead, I shall rest my body
in this here chalk outline.'', and so he did. The shooter was soon
arrested for manslaughter. Through a swift trial, with abundant
eyewitnesses, he was sentenced to solitary confinement, with
madness-alleviating torture. Lucian died in that prison at age
sixty-seven.

Lucian wakes up on a bed, in a familiar room. Green and black flower
pattern, of course, this is where he waited before the audition with
Astrophel. Checking his pocket watch, Lucian finds it is fifty-nine
minutes after midnight, and so stands up from the bed. The lodging
promptly rotates around, revealing that Clerval had been resting on the
reverse side.

Upon Clervall's awakening from his slumber, the duo is greeted by a
familiar sight, a raven had roosted upon the bedhead. It seems that
Saber had come to introduce himself. He seems to have as many bandages
as he has hairs, a long flowing red cloak hiding surely yet more ravens
and to top off the look, he had an animal skull attached to his head. He
explains that the next event will be quite simple and that their entire
purpose is to banish his pet. This is Strisk, Saber exclaimed soaring to
the ceiling and performing a backflip onto it's back.

Clervall stated in his always calm and calming voice, ``RUN''. We didn't
even think, running through the nearest piece of wall into a hallway
complex. We managed to evade the beast for a few years, even managing to
find some information on how we could be able to dispose of Strisk. He
could still be behind any corner, waiting\ldots{} at any time or
thought. Every time he'd catch us, the pain was less unbearable. We
tried, but one day, it came. I was on my back, Strisk devouring my body,
which instantaneously grew back and repaired. This was quite preferable
to running. The physical pain was nothing when compared to what I had
suffered through, up to that point, however, it seems that the human
psyche can only take so much pain before weakening, if only they made
that part immortal as well. But being immortal, wasn't preferable in
this situation, it was a curse, to make me able to experience what
really mattered to them. As I lay there being feasted upon, in form by
Strisk, in spirit by the rest of Jadewill, contemplating these
circumstances, a flash of light appears next to Saber riding on the back
of Strisk. The light instantaneously materialises into Callidora,
slamming with inhuman force into the side of Strisk's head, knocking off
Saber through the sheer force of impact. ``I will not let you enjoy
another second of this, for what you have done Astrohpel'', shouts a
very discontent Callidora at the top of her lungs. Before anyone could
even begin to contemplate the thought of beginning to consider what to
do next, reality around me started to show cracks. Through it I began to
see my room, a place I had not seen in an hour and ten minutes or over
fifty years, I have no idea. No matter how long it had taken, I was most
certainly returning there. Falling bluntly into my recliner.

It started with immense pain, my heard started bleeding. I thrashed
around for a few minutes. Then, bite marks started to show. I am glad or
sad, I don't know, I wished to die, but now I cling to life with all my
might, that is the nature of man. As I lay here with all these wounds, I
contemplate if I truly won. I would not have survived it by any chance,
but Lucilla's death shortened my suffering. Death lead to death.
However, this death, was the greatest gift.
