\chapter{When Fire reigns}

Thousands of years of ancestry now lie uncovered, closer than ever,
glaring him in the eyes. Inviting the lost soul to take refuge in the
few remains of what they once bared. The burdens of all he saw seemed to
him as to shift unto his heart, with every step he grew more tired, more
scared of this world. One he had helped build, but one he did not want.
Vines surround him clutching his feet with all the might of centuries
untold as if burdens his own had not been enough to bare. He endures for
his journey's end is not far away. What he strives for, had been decades
untended to, nature's grasp had dragged its legends deep into the
ground. Stairs crumbled under every step he took, countless times he
thought he'd fall, but this he did not care for, not for a single
moment, he had not another place left to go, no other purpose. On his
journey he passed countless statues, nature had taken their faces.
Though he still recognized many, none of them could help him now. The
gateway to this sanctuary once-great now lays broken and twisted. His
mere presence disturbs this crypt lost in time. He placed his foot unto
the tiled balcony which weaved his step into a melody announcing his
arrival as it echoed through the crypt. He approaches\ldots{} gently
raising his hand, inciting the rose and vine laden door to open. The
scape of rust and degraded wood almost quelling the sounds of falling
metal echoed once again throughout the tower. He entered the room, his
feet disturbing layers of leaves, ash and dust. He had never come here,
he had never been allowed. Overhead, cowering, sat many doves, he
greeted them, for now, they shared fate. He passed torn paintings, old
carved stone and many crosses. The room had once been decorated with
beautiful wallpaper gold-laden with icons of religion and nature, even
these were now but a reminder of a bygone world. He approached an old
altar on each side of which stood the statue of an angel, one clutching
a quill and the other a piece of parchment. He approached and as he
knelt down one of the doves flew down unto the altar, raising its head
in anticipation. The old man dropped to the ground crying and begged for
forgiveness, for the world to be saved, for the world to not suffer for
his sins. He pleaded the struggle would come to an end. The dove flew
outside the tower from whence the man came and picked an olive branch,
then soared off the tower. The old man's soul was at rest, he followed
the dove outside and having completed his journey he took a step off the
ledge.
