\chapter{The Will to Tango - Drafting}

``So\ldots{} what do we do about the book?'' said Cordelia looking
around the dimly lit room, where several characters sat each in a deep
leather armchair, each of their faces illuminated by a fire shimmering
in the corner of the room. ``Every one of us wants it and if one were to
take it by force, the others would quickly overwhelm him'' continues
Ezekiel. A very old man, his image covered with many a grey hair and
scar, in a deep vibrant voice suggests, ``Whatever would you crave in
return for surrendering it Ezekiel?''. Perhaps if the person lost an arm
and a leg I might be entertained enough. Saber starts to say something
but is swiftly cut off by Ezekiel, ``You are in no position to make
demands Saber, I'm not afraid to take you on, the only ones here who can
make demands except Astrophel is Callidora and Cordelia''. ``How about
two castles then?'', says Cordelia. Callidora makes an effort to look in
the direction of Cordelia, even though her blindfold makes it a slightly
problematic task, ``Truly, you would yield your claim for the low price
of two castles?''. ``Each'', adds Cordelia. ``The proposition is highly
reasonable'', replies Callidora, but I must conclude this debate for the
time being for Astrophel seems to be somewhat Drowsy and I myself would
greatly benefit from a slight whiff of fresh air. Cordelia snaps at
Cordelia, ``And who will guard the book if we're out?''. Saber shyly and
now with a slightly startled gaze at Ezekiel, suggests ``Since Callidora
has limited omnipotence she will be able to keep oversight of the book,
while I keep an eye on her''. ``Yep, sounds swell'', exclaims Ezekiel
driving his palms right into the old carved wooden door; after the loud
collision Ezekiel left the room with Cordelia and Saber in tow.
Callidora sighs softly and beckons her butler close, whispering in his
ear ``Sabien, would you mind doing something about that clock, please''.
Sabien bows deeply and humbly, ``Yes, ma'am''. ``Shall we?'', asks
Clerval with hand extended towards Callidora. ``Thank you, I am able to
stand by myself but walking around without colliding with all the walls
is the arduous task, safe your care for later.''. And so, Clerval and
Saber walk slowly, leading Callidora through the halls towards a moonlit
corridor with a wall full of windows, all of which are now open.

Ezekiel and Cordelia may have a terrible temper, but they sure know how
to make a good draft. The walls are lined with classic wooden carvings
with depictions of torture, every stake a different carving. Some are
lined with twisted metal reinforcements shaped into giant snake
skeletons topped with animal sculptures of a cat, a winged man, a raven
and a lion. ``Have you ever been here before Callidora?'', Clerval
inquires. ``The Jadewill Mansion's then residents never let anyone enter
other that mortals.''. ``However I heard that you met the family head,
what happened to them?'', Clerval asked on. Callidora smirking
continues, ``After Lucilla Jadewill's death, her sister massacred the
Jadewill family in retribution, not much is known about the incident.
Though without her father's centuries of wisdom, which I must say he did
not express in his manners even slightly, she could not tend to the
mansion and wasn't able to carry on her clan's legacy. The Jadewill
family was no more.''. If you met him\ldots{} how old are you Callidora?
Oh that is no question to ask of a lady like myself. You are utmost
correct on that Callidora, I apologize. Callidora turns her head in the
general direction of Clerval, informing him that she wants to advise him
on a matter very important, ``The Jadewill lineage is exceptionally
longer than you think and considering the mansion's history the souls it
claimed must be incomprehensible. None of us has the business of owning
such a thing.''.

Saber raises his hand to stop the trio. ``What might it be Saber?'',
asks Clerval, ``wait\ldots{} ohh, what is that smell?''. ``This way'',
signs Saber. The three run down the corridor to a half-open door. Saber
lightly nudges the door with the rear of his hand. ``Keep your eyes on
the book'' shouts Clerval. Callidora gently nodding. Saber catches a
glimpse of what is inside and turns around to vomit on the floor.
Callidora tenderly addresses the vomiting pile of gibbering nonsense on
the floor, ``Oh we do have to do something about that weak stomach of
yours, now don't we Saber?''. Clerval peers inside just to be met with
Astrophel's face. Continuing upwards with his gaze he comes to see that
his upper body is completely wrapped in spiked chains, shred absolutely
to pieces and bleeding. Clerval momentarily pauses pondering whether the
part covered in chains is the upper or lower body, considering the chain
is attached to the ceiling causing Astrophel's lifeless body to gently
sway upside down in the wind coming through the door. Ezekiel, hearing
the commotion, tears in and promptly slips on the blood.

Back in the room, now shorter by one very old man.
